Quotient maps and configuration spaces of hard disks

### 2022-02-09 manuscript/main.tex
text added to explain base vs quotient spaces - introduction
critical point explanation in morse theory section updated

Roughly speaking, a quotient map sends a set of points in the base configuration space differing only by the action of a symmetry group to a single point in the quotient space. That is, the quotient map collects configurations with identical physical properties into equivalence classes, and the quotient space describes how the equivalence classes should be related to one another to preserve sensible notions of similarity. The equivalence classes studied by Ritchey \cite{ritcheyphd} effectively define a set of quotient maps and quotient spaces that are studied in more detail here.

@@

\red{At this point, it is worth mentioning that the critical points considered in this work are not the critical points of the potential energy surface on the configuration space $\Gamma(n,\rho)$, but the critical points of the tautological function $\tau$ on $\Lambda(n)$. Observe that $\Gamma(n,\rho)$ is some particular subset of $\Lambda(n)$ containing the points in $\Lambda(n)$ such that no overlapping will occur if disks of radius $\rho$ are placed to these points. In the context of Morse theory, the critical points of $\tau$ are then the locations where the topology of $\Lambda(n)$ (hence $\Gamma(n,\rho)$) changes. Keeping these in mind, the potential energy of each point in $\Gamma(n,\rho)$ is necessarily zero since they are guaranteed to be non-overlapping.}

>>>>

Roughly speaking, a quotient map sends a set of points in the base configuration space differing only by the action of a symmetry group to a single point in the quotient space. That is, the quotient map collects configurations with identical physical properties into equivalence classes, and the quotient space describes how the equivalence classes should be related to one another to preserve sensible notions of similarity. The equivalence classes studied by Ritchey \cite{ritcheyphd} effectively define a set of quotient maps and quotient spaces that are studied in more detail here. \red{In this work, a quotient space always refers to a new space generated by quotienting the base configuration space under the action of various symmetry groups. The detailed definitions of these spaces are provided in the following sections.}

@@

\red{At this point, it is worth mentioning that the critical points considered in this work are not the critical points of the potential energy surface on the configuration space $\Gamma(n,\rho)$, but the critical points of the tautological function $\tau$ on $\Lambda(n)$. Observe that $\Gamma(n,\rho)$ is some particular subset of $\Lambda(n)$ containing the points in $\Lambda(n)$ such that no overlapping will occur if disks of radius $\rho$ are placed to these points. Keeping these in mind, the potential energy of each point in $\Gamma(n,\rho)$ is necessarily zero since they are guaranteed to be non-overlapping. In the context of Morse theory, the critical points of $\tau$ are then the locations where the topology of $\Lambda(n)$ (hence $\Gamma(n,\rho)$) changes.}
